Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-01-10 Paper.Rmd
fixing all table appearence

row.names(tab_multivar_summary)<-NULL
library(kableExtra)
library(dplyr)
library(tibble)
dt <- tibble(
            Description = c("1. Location pairs (excluding self comparisons)",
           "2. Number of non-independent pairs",
           "3. Number of pairs with non-N copula as best fit",
           "4. Average AIC-weights of best-fitting copulas across location pairs",
           "5. Average AIC-weights of N copula across pairs",
           "6. Number of well-fitting location pairs",
           "7. 2.5th and 97.5 quantiles of model-avg. lower-tail dependence",
           "8. 2.5th and 97.5th quantiles of model-avg. upper-tail dependence",
           "9. Percent pairs showing stronger lower tail dependence",
           "10. 95% CI of average P_l - P_u across all location pair")
           )

@@

knitr::kable(tab_multivar_summary, 
             format="latex", 
             short.caption = "Summary of results for multivariate data sets"
             caption = "Summary of results for multivariate data-sets. Rows 3-9 of the table were computed for the non-independent pairs (row 2) only; row 10 was for all location pairs. A well-fitting location pair (row 6) was one for which the best-fitting copula had $p$-values $>0.01$ for both the Cramer-von Mises and Kolmogorov-Smirnov goodness of fit tests. \\label{tab_multivar_summary}",
             booktabs=T, linesep = "\\addlinespace",
             col.names = c(" ","Green-spruce aphid's count",
                        "Leaf-plum curling aphid's firstflight",
                        "Ceratium furca's count","Methane-flux")
             )%>%column_spec(2:5,width="2.5cm")%>%
             column_spec(1, width = "7cm")%>%kable_styling(latex_options = "basic",position = "center")
```

>>>>

row.names(tab_multivar_summary)<-NULL
library(kableExtra)
library(dplyr)
library(tibble)
dt <- tibble(
            Description = c("1. Location pairs (excluding self comparisons)",
           "2. Number of non-independent pairs",
           "3. Number of pairs with non-N copula as best fit",
           "4. Average AIC-weights of best-fitting copulas across location pairs",
           "5. Average AIC-weights of N copula across pairs",
           "6. Number of well-fitting location pairs",
           "7. 2.5th and 97.5 quantiles of model-avg. lower-tail dependence",
           "8. 2.5th and 97.5th quantiles of model-avg. upper-tail dependence",
           "9. Percent pairs showing stronger lower tail dependence",
           "10. 2.5th and 97.5th quantiles of $<$P$_{l}$ - P${_u}$$>$ across all location pair")
           )

@@

knitr::kable(tab_multivar_summary, 
             format="latex", escape = F,
             caption.short = "Summary of results for multivariate data sets",
             caption = "Summary of results for multivariate data-sets. Rows 3-9 of the table were computed for the non-independent pairs (row 2) only; row 10 was for all location pairs. A well-fitting location pair (row 6) was one for which the best-fitting copula had $p$-values $>0.01$ for both the Cramer-von Mises and Kolmogorov-Smirnov goodness of fit tests. \\label{tab_multivar_summary}",
             booktabs=T, linesep = "\\addlinespace",
             col.names = c(" ","Green-spruce aphid's count",
                        "Leaf-plum curling aphid's firstflight",
                        "Ceratium furca's count","Methane-flux")
             )%>%column_spec(2:5,width="2.5cm")%>%
             column_spec(1, width = "7cm")%>%kable_styling(latex_options = "basic",position = "center")
```

### 2019-01-10 SupportingInformation.Rmd
fixing all table appearence

<!--Show the statistical results in a table-->
```{r tab_count_resamp,echo=F,results="markup"}
s<-stat_aphid_count$numericdf[,c(3,2,4)]
colnames(s)<-c("Lower 95% CI", "Mean", "Upper 95% CI")
rownames(s)<-c("Spearman","Kendall","cor_l","cor_u","P_l","P_u","D^2_l","D^2_u","cor_l - cor_u","P_l - P_u","D^2_u - D^2_l")
knitr::kable(round(s,3),
             format = "latex",linesep = "",
             caption.short="Results for nonparametric statistics, green spruce aphid abundance data",
             caption = "Average values of statistics across all locations pairs and confidence intervals based on spatial resampling for green spruce aphid abundance data.\\label{tab_count_resamp}",
             booktabs=TRUE)
```

@@

<!--display the main statistical results in a table-->
```{r tab_ff_resamp,echo=F,results="markup"}
s<-stat_aphid_ff$numericdf[,c(3,2,4)]
colnames(s)<-c("Lower 95% CI", "Mean", "Upper 95% CI")
rownames(s)<-c("Spearman","Kendall","cor_l","cor_u","P_l","P_u","D^2_l","D^2_u","cor_l - cor_u","P_l - P_u","D^2_u - D^2_l")
knitr::kable(round(s,3),
             format = "latex",linesep = "",
             caption.short="Results for nonparametric statistics, leaf-curling plum aphid first flight data",
             caption = "Average values of statistics across all location pairs and confidence intervals based on spatial resampling for leaf-curling plum aphid first flight data.\\label{tab_ff_resamp}",
             booktabs=TRUE)
```

@@

<!--display the main statistical results in a table-->
```{r tab_pns_resamp,echo=F,results="markup"}
s<-stat_plankton_north_sea$numericdf[,c(3,2,4)]
colnames(s)<-c("Lower 95% CI", "Mean", "Upper 95% CI")
rownames(s)<-c("Spearman","Kendall","cor_l","cor_u","P_l","P_u","D^2_l","D^2_u","cor_l - cor_u","P_l - P_u","D^2_u - D^2_l")
knitr::kable(round(s,3),
             format = "latex",linesep = "",
             caption.short="Results for nonparametric statistics, \\textit{Ceratium furca} abundance data",
             caption = "Average values of statistics across all locations pairs and confidence intervals based on spatial resampling for \\textit{Ceratium furca} abundance data.\\label{tab_pns_resamp}",
             booktabs=TRUE)
```

@@

<!--display the main statistical results in a table-->
```{r tab_methane_resamp,echo=F,results="markup"}
s<-stat_methane$numericdf[,c(3,2,4)]
colnames(s)<-c("Lower 95% CI", "Mean", "Upper 95% CI")
rownames(s)<-c("Spearman","Kendall","cor_l","cor_u","P_l","P_u","D^2_l","D^2_u","cor_l - cor_u","P_l - P_u","D^2_u - D^2_l")
knitr::kable(round(s,3),
             format = "latex",linesep = "",
             caption.short="Results for nonparametric statistics, methane flux data",
             caption = "Average values of statistics across all locations pairs and confidence intervals based on spatial resampling for methane flux data.\\label{tab_methane_resamp}",
             booktabs=TRUE)
```

>>>>

<!--Show the statistical results in a table-->
```{r tab_count_resamp,echo=F,results="markup"}
s<-stat_aphid_count$numericdf[,c(3,2,4)]
sc<-as.data.frame(c("Spearman","Kendall","cor$_{l}$","cor$_{u}$","P$_{l}$","P$_{u}$","D$_{l}^2$","D$_{u}^2$",
                    "cor$_{l}$ - cor$_{u}$","P$_{l}$ - P$_{u}$","D$_{u}^2$ - D$_{l}^2$"))
s<-cbind(sc,s)
colnames(s)<-c("","2.5th quantile", "Mean", "97.5th quantile")
knitr::kable(s,
             format = "latex",linesep = "", escape = F,align="c",
             caption.short="Results for nonparametric statistics, green spruce aphid abundance data",
             caption = "Average values of statistics across all locations pairs and confidence intervals based on spatial resampling for green spruce aphid abundance data.\\label{tab_count_resamp}",
             booktabs=TRUE)
```

@@

<!--display the main statistical results in a table-->
```{r tab_ff_resamp,echo=F,results="markup"}
s<-stat_aphid_ff$numericdf[,c(3,2,4)]
sc<-as.data.frame(c("Spearman","Kendall","cor$_{l}$","cor$_{u}$","P$_{l}$","P$_{u}$","D$_{l}^2$","D$_{u}^2$",
                    "cor$_{l}$ - cor$_{u}$","P$_{l}$ - P$_{u}$","D$_{u}^2$ - D$_{l}^2$"))
s<-cbind(sc,s)
colnames(s)<-c("","2.5th quantile", "Mean", "97.5th quantile")
knitr::kable(s,
             format = "latex",linesep = "", escape = F,align="c",
             caption.short="Results for nonparametric statistics, leaf-curling plum aphid first flight data",
             caption = "Average values of statistics across all location pairs and confidence intervals based on spatial resampling for leaf-curling plum aphid first flight data.\\label{tab_ff_resamp}",
             booktabs=TRUE)
```

@@

<!--display the main statistical results in a table-->
```{r tab_pns_resamp,echo=F,results="markup"}
s<-stat_plankton_north_sea$numericdf[,c(3,2,4)]
sc<-as.data.frame(c("Spearman","Kendall","cor$_{l}$","cor$_{u}$","P$_{l}$","P$_{u}$","D$_{l}^2$","D$_{u}^2$",
                    "cor$_{l}$ - cor$_{u}$","P$_{l}$ - P$_{u}$","D$_{u}^2$ - D$_{l}^2$"))
s<-cbind(sc,s)
colnames(s)<-c("","2.5th quantile", "Mean", "97.5th quantile")
knitr::kable(s,
             format = "latex",linesep = "", escape = F,align="c",
             caption.short="Results for nonparametric statistics, \\textit{Ceratium furca} abundance data",
             caption = "Average values of statistics across all locations pairs and confidence intervals based on spatial resampling for \\textit{Ceratium furca} abundance data.\\label{tab_pns_resamp}",
             booktabs=TRUE)
```

@@

<!--display the main statistical results in a table-->
```{r tab_methane_resamp,echo=F,results="markup"}
s<-stat_methane$numericdf[,c(3,2,4)]

#rownames(s)<-c("Spearman","Kendall","cor_l","cor_u","P_l","P_u","D^2_l","D^2_u","cor_l - cor_u","P_l - P_u","D^2_u - D^2_l")

sc<-as.data.frame(c("Spearman","Kendall","cor$_{l}$","cor$_{u}$","P$_{l}$","P$_{u}$","D$_{l}^2$","D$_{u}^2$",
                    "cor$_{l}$ - cor$_{u}$","P$_{l}$ - P$_{u}$","D$_{u}^2$ - D$_{l}^2$"))
s<-cbind(sc,s)
colnames(s)<-c("","2.5th quantile", "Mean", "97.5th quantile")
knitr::kable(s,
             format = "latex",linesep = "", escape = F,align="c",
             caption.short="Results for nonparametric statistics, methane flux data",
             caption = "Average values of statistics across all locations pairs and confidence intervals based on spatial resampling for methane flux data.\\label{tab_methane_resamp}",
             booktabs=TRUE)
```
